### 2008-03-21 trunk/Papers/dl-gre-08/bisim.tex
the rest of the edits we discussed

\todo{formula preservation} A key notion in description logics that we
will use here is \emph{similarity}.  For any description logic $\gL$,
we will say that an individual $i$ is \emph{\gL-similar} to $i'$ in a
given model $\gM$ if for any formula $\varphi \in \gL$ such that $i
\in \interp{\varphi}$, we also have $i' \in \interp{\varphi}$.
Equivalently, there is no $\gL$-formula that holds of $i$ but not of
$i'$.  We say that the \emph{\gL-similarity set} of some individual
$i$ is the set of all individuals to which $i$ is \gL-similar.

>>>>

Below, we will use a key notion of formula preservation that we call
\emph{similarity}.  For any description logic $\gL$, we will say that
an individual $i$ is \emph{\gL-similar} to $i'$ in a given model $\gM$
if for any formula $\varphi \in \gL$ such that $i \in
\interp{\varphi}$, we also have $i' \in \interp{\varphi}$.
Equivalently, there is no $\gL$-formula that holds of $i$ but not of
$i'$.  We say that the \emph{\gL-similarity set} of some individual
$i$ is the set of all individuals to which $i$ is \gL-similar.

### 2008-03-21 trunk/Papers/dl-gre-08/related.tex
the rest of the edits we discussed

Perhaps closest in spirit to our approach is 
Krahmer et al.\ graph algorithm~\shortcite{Krahmer2003}, which also computes formulas by
extending them successively.  Interestingly, Krahmer et al.\ themselves
discuss the possibility of a logic based approach by considering graph as
models of a logical language and using logical tools.  They explicitly
mentions hybrid logics which can be seen as very expressive description
logics~\cite{arec:hybr05b}.
Their algorithm, though, focuses on
reference to a single individual and has NP-complete worst-case
complexity.

@@

Where our approach breaks new ground is in the way these formulas
are computed: It successively
refines a decomposition of the domain into subsets.  In this way, it
is reminiscent of the Incremental Algorithm, which in fact can be seen
as the special case of the \el\ algorithm for the non-relational case.
However, unlike
\newcite{dale91:_gener_refer_expres_invol_relat} and its successors,
we do not have to take special precautions to avoid infinite regress. While Dale
and Haddock's algorithm attempts to generate a RE for a single
individual for successive individuals in the model, our algorithms
consider all individuals in parallel and are guaranteed to always terminate.

>>>>

Where our approach breaks new ground is in the way these formulas are
computed: It successively refines a decomposition of the domain into
subsets.  In this way, it is reminiscent of the Incremental Algorithm,
which in fact can be seen as the special case of the \el\ algorithm
for the non-relational case.  However, unlike
\newcite{dale91:_gener_refer_expres_invol_relat} and its successors,
such as \newcite{kelleher06:_increm_gener_of_spatial_refer},
we do not have to take special precautions to avoid infinite
regress. While Dale and Haddock's algorithm attempts to generate a RE
for a single individual for successive individuals in the model, our
algorithms consider all individuals in parallel and are guaranteed to
always terminate.

Perhaps closest in spirit to our approach is Krahmer et al.'s graph
algorithm~\shortcite{Krahmer2003}, which also computes REs by
extending them successively.  However, their subgraphs go beyond the
expressive power of \alc\ in that they can distinguish between ``the
dog that bites a dog'' and ``the dog that bites itself''.  The price
they pay for this increase in expressive power is an NP-complete
worst-case complexity.  Interestingly, Krahmer et al.\ themselves
discuss the possibility of seeing their subgraphs as formulas of
hybrid logic which are satisfied at the points where the subgraph can
be embedded; and hybrid logics can be seen as very expressive
description logics~\cite{arec:hybr05b} as well.

@@
